---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# wang13: Wang et al.'s (2013) Roughness Model

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/pmcharrison/wang13.svg?branch=master)](https://travis-ci.org/pmcharrison/wang13)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/pmcharrison/wang13?branch=master&svg=true)](https://ci.appveyor.com/project/pmcharrison/wang13)
[![Coverage status](https://coveralls.io/repos/github/pmcharrison/wang13/badge.svg)](https://coveralls.io/r/pmcharrison/wang13?branch=master)

The `wang13` R package implements Wang et al.'s (2013) roughness model.

## Installation

Within R, you can install the current version of `wang13` from Github as follows:

``` r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("wang13")
```

## Usage

Higher scores correspond to greater roughness. 

```{r}
library(wang13)

# Octave
roughness_wang(c(60, 72))

# Semitone
roughness_wang(c(60, 61))
```

## References

Wang, Y. S., Shen, G. Q., Guo, H., Tang, X. L., & Hamade, T. (2013). Roughness modelling based on human auditory perception for sound quality evaluation of vehicle interior noise. Journal of Sound and Vibration, 332(16), 3893–3904. https://doi.org/10.1016/j.jsv.2013.02.030
